Staged Abstract Interpreters

### 2018-11-17 paper/60_eval.tex
revise

We have designed, implemented and evaluated a prototype abstract interpreter for Scheme.
In order to compare results, our prototype includes both staged and unstaged versions of
the abstract interpreter doing the same control flow analysis.

Our evaluations have shown that the staged abstract interpreter performs well in general.
Particularly in some interesting cases that are considered to be the worst case scenario
in the control flow analysis, the staged version outperforms the unstaged abstract 
interpreter by a wide margin.

@@

\subsection{Performance}
We performed our 
For each benchmark program, we ran our prototype abstract interpreters, both unstaged and staged.

\subsubsection{Baselines}
Small-step AAM

Big-step ADI

OAAM with AC \cite{Boucher:1996:ACN:647473.727587, Johnson:2013:OAA:2500365.2500604}

Benchmarks and other reference implementations: \url{https://github.com/ilyasergey/reachability}.

\subsection{Compositionality}

>>>>

To evaluate the performance can be improved through staging, we use the abstract
interpreter demonstrated in the paper to analyze some Scheme programs. We implement
a desugaring transformation for a large subset of scheme that transforms into the
small language we used in the paper.
We use the same generic interface with a 0-CFA-like abstraction, and the unstage abstract
interpreter forms the baseline.

All of our evaluation benchmarks were performed on an Ubuntu 16.04 LTS (Linux kernel 4.4.0)
machine with 4 Intel Xeon Platinum 8168 CPU at 2.7GHz and 3 TiB of RAM.
Although the machine has 96 cores and 192 threads in total,
the abstract interpreters only use one thread to run all the benchmark programs.

@@

\subsection{Performance}

For each benchmark program, we ran our prototype abstract interpreters, both unstaged and staged.
\todo{Figure show data.}

Our evaluations have shown that the staged abstract interpreter performs well in general.
Particularly in some interesting cases that are considered to be the worst case scenario
in the control-flow analysis, the staged version outperforms the unstaged abstract 
interpreter by a wide margin.
